Measuring individual differences in the understanding of gaze cues

### 2023-05-31 paper/manuscript.Rmd
make ready for resubmission

```{r splithalf}
splithalf <- readRDS(file = "../saves/tango-splithalf-table.rds")
```

@@

```{r hedge_retest_correlationcoefficients}
hedge_retest_correlationcoefficients <- readRDS(file = "../saves/tango-hedge-retest-correlationcoefficients.rds")
```

>>>>

```{r splithalf}
splithalf <- readRDS(file = "../saves/tango_splithalf_table.rds")
```

@@

```{r hedge_retest_correlationcoefficients}
hedge_retest_correlationcoefficients <- readRDS(file = "../saves/tango_hedge_retest_correlationcoefficients.rds")
```
